### 2021-08-13 paper/paper.tex
Move statement about compiler speeds to the appropriate section
Add plural "s" for better reading flow
Simplify statement

All simulations for the performance comparison were run on the HPC system Tetralith
provided by the Swedish National Infrastructure for Computing (SNIC).
Each node of Tetralith has two sockets, each with an Intel(R) Xeon(R) Gold 6130 @ 2.10GHz with 96GiB of memory.
FLUXO was compiled using the Intel compiler suite v18.0.3 and \trixi used Julia v1.6.1.
The serial performance results were obtained on a single core.
We ran each configuration of a particular physical setup, polynomial degree, and solver type
for each code five times, taking the smallest value from each for the comparison results.

@@

From these results, it is clear that \trixi is more than 2x faster for the compressible Euler equations
and more than 1.5x faster for the ideal MHD equations than the Fortran code FLUXO.
We ran the same PID tests in FLUXO compiled with GCC v6.4.0 but found that
the version compiled using Intel was between \SI{5}{\percent} to \SI{23}{\percent} faster.
Thus, only results from the Intel compiler are included.
It is also possible to see the additional computational effort for the entropy-conservative flux
differencing DG methods for both physical systems. This is because the numerical fluxes are more
expensive in
terms of computational cost, and require special care to optimize their performance~\cite{hendrik_blog}.
We reiterate that both codes implement the same numerical nodal DG methods on curvilinear meshes used in these tests.
This demonstrates the suitability of Julia for this kind of simulation-focused scientific computing.

While our Julia code is faster than the mature HPC Fortran code FLUXO for this non-trivial
example, we do not claim that Julia is generally faster than Fortran, C, or C++.
Instead, we would like to emphasize that Julia code can be \emph{at least
as fast} as code written in these traditional scientific computing languages.
Further, we expect to be able to achieve similar performance with either language
by spending enough time and effort to optimize the respective code.
\trixi owes its performance optimizations in part to the code introspection and
profiling tools available in Julia. Similar tools used to optimize the performance in other
languages are often not as easy to use as their Julia counterparts.

Finally, the different mesh types available in \trixi allow further optimizations.
For example, if the computational domain is essentially a cube (or square, line)
without need for curvilinear coordinates, the Cartesian \lstinline{TreeMesh} can
be used. Depending on the relative computational effort of the discretization
(such as the polynomial degree and the choice of the volume terms), the
Cartesian \lstinline{TreeMesh} can be \SI{10}{\percent} to \SI{25}{\percent}
more efficient than the curvilinear meshes in \trixi.

>>>>

All simulations for the performance comparison were run on the HPC system Tetralith
provided by the Swedish National Infrastructure for Computing (SNIC).
Each node of Tetralith has two sockets, each with an Intel(R) Xeon(R) Gold 6130 @ 2.10GHz with 96GiB of memory.
FLUXO was compiled using the Intel compiler suite v18.0.3 and \trixi used Julia v1.6.1.
The serial performance results were obtained on a single core.
We ran each configuration of a particular physical setup, polynomial degree, and solver type
for each code five times, taking the smallest value from each for the comparison results.
We ran the same PID tests in FLUXO compiled with GCC v6.4.0 but found that
the version compiled using Intel was between \SI{5}{\percent} to \SI{23}{\percent} faster.
Thus, only results from the Intel compiler are included.

@@

From these results, it is clear that \trixi is more than 2x faster for the compressible Euler equations
and more than 1.5x faster for the ideal MHD equations than the Fortran code FLUXO.
It is also possible to see the additional computational effort for the entropy-conservative flux
differencing DG methods for both physical systems. This is because the numerical fluxes are more
expensive in
terms of computational cost, and require special care to optimize their performance~\cite{hendrik_blog}.
We reiterate that both codes implement the same numerical nodal DG methods on curvilinear meshes used in these tests.
This demonstrates the suitability of Julia for this kind of simulation-focused scientific computing.

While our Julia code is faster than the mature HPC Fortran code FLUXO for this non-trivial
example, we do not claim that Julia is generally faster than Fortran, C, or C++.
Instead, we would like to emphasize that Julia code can be \emph{at least
as fast} as code written in these traditional scientific computing languages.
Further, we expect to be able to achieve similar performance with either language
by spending enough time and effort to optimize the respective codes.
\trixi owes its performance optimizations in part to the code introspection and
profiling tools available in Julia. Similar tools used to optimize the performance in other
languages are often not as easy to use as their Julia counterparts.

Finally, the different mesh types available in \trixi allow further optimizations.
For example, if the computational domain is essentially a cube (or square, line)
without need for curvilinear coordinates, the Cartesian \lstinline{TreeMesh} can
be used. Depending on the particular choice of discretization methods, the
Cartesian \lstinline{TreeMesh} can be \SI{10}{\percent} to \SI{25}{\percent}
more efficient than the curvilinear meshes in \trixi.
